Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-07-17 abstract.tex
new production figure + addition of symetric adjectif when refering to cascade design

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades, contributing to more effective
international safeguards designs and approaches.  While it is straightforward to
design an enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition to the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

Following a description of each method and an evaluation of differences between
each approach, this work compares the results produced by these methods within
scenarios involving misuse of enrichment cascades simulated using the dynamic
nuclear fuel cycle simulator, Cyclus.

>>>>

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades, contributing to more effective
international safeguards designs and approaches.  While it is straightforward to
design an symmetric enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition to the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

Following a description of each method and an evaluation of differences between
each approach, this work compares the results produced by these methods within
scenarios involving misuse of symmetric enrichment cascades simulated using the dynamic
nuclear fuel cycle simulator, Cyclus.

### 2018-07-17 dis_clusion.tex
new production figure + addition of symetric adjectif when refering to cascade design

This work has investigated the possibility to chain centrifuge enrichment
cascades that are designed to enrich uranium for commercial reactors in order to
produce \gls{HEU}, instead. Three methods have been implemented to model enrichment
cascade behavior when fed with different uranium enrichment than the designed
enrichment.

>>>>

This work has investigated the possibility to chain centrifuge enrichment
cascades that are designed to enrich uranium for commercial reactors in order to
produce \gls{HEU}, instead. Three methods have been implemented to model
symmetric enrichment cascade behavior when fed with different uranium enrichment
than the designed enrichment.

### 2018-07-17 motivation.tex
new production figure + addition of symetric adjectif when refering to cascade design

With the current international tensions regarding enrichment capabilities, this
work aims to measure the effectiveness of an enrichment cascade when used outside of
its designed scope and quantify the attractiveness of such way to build up
significant quantity of \gls{HEU}.

>>>>

With the current international tensions regarding enrichment capabilities, this
work aims to measure the effectiveness of an symmetric enrichment cascade when
used outside of its designed scope and quantify the attractiveness of such way
to build up significant quantity of \gls{HEU}.

### 2018-07-17 theory.tex
new production figure + addition of symetric adjectif when refering to cascade design

The cascade is built as an ideal cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ represent the feed to product and the feed to
tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

@@

The design of the cascade is performed through 2 steps.  First one determines
the configuration and number of stages, adding stages until the product assay of
the final stage is greater or equal the product targeted assay, and similarly
the tails assay is less or equal the tails desired assay.  This determines the
number of enriching and stripping stages as well as their enrichment properties
($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).

>>>>

The cascade is built as a ideal symmetric cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ represent the feed to product and the feed to
tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

@@

The design of the ideal symmetric cascade is performed through 2 steps.  First
one determines the configuration and number of stages, adding stages until the
product assay of the final stage is greater or equal the product targeted assay,
and similarly the tails assay is less or equal the tails desired assay.  This
determines the number of enriching and stripping stages as well as their
enrichment properties ($N_{i}$, $N'_{i}$, $N''_{i}$,$\theta_{i}$i).
